---
title: "P1805_hw1_ys3924"
author: "YISU"
date: "2024-09-21"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
```

## Read in penguins data

Read in penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
```


## Write a short description of the penguins dataset

```{r}
# Variable names
key_variables <- colnames(penguins)
# Number of rows
num_rows <- nrow(penguins)
# Number of columns
num_columns <- ncol(penguins)
# Mean flipper length
mean_flipper_length <- mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
# Penguins species
penguins_species <- unique(pull(penguins, species))
```

The penguins dataset contains information of different penguins species: `r penguins_species`, with `r num_rows` rows and `r num_columns` columns. The key variables are `r key_variables`. The mean flipper length is `r mean_flipper_length`.


## Create the scatterplot

Use ggplot to create the scatterplot.

```{r, warning=FALSE, message=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length")
# Saving the scatterplot
ggsave("penguins_scatterplot.png")
```

