---
title: "P1805_hw1_ys3924"
author: "YISU"
date: "2024-09-21"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
```

## Read in penguins data

Read in penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
```


## Write a short description of the penguins dataset

```{r}
# Variable names
key_variables <- colnames(penguins)
# Number of rows
num_rows <- nrow(penguins)
# Number of columns
num_columns <- ncol(penguins)
# Mean flipper length
mean_flipper_length <- mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
# Penguins species
penguins_species <- unique(pull(penguins, species))
```

The penguins dataset contains information of different penguins species: `r penguins_species`, with `r num_rows` rows and `r num_columns` columns. The key variables are `r key_variables`. The mean flipper length is `r mean_flipper_length`.


## Create the scatterplot

Use ggplot to create the scatterplot.

```{r, warning=FALSE, message=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length")
# Saving the scatterplot
ggsave("penguins_scatterplot.png")
```


## Create the data frame

Create the data frame by using the tibble function.
```{r}
set.seed(1805)
df = tibble(
  vec_sample = rnorm(10, 0, 1),
  vec_logical = vec_sample > 0,
  vec_char = c("this", "is", "ds", "class", "for", "master", "student", "in", "c", "u"),
  vec_factor = factor(sample(c("low", "med", "high"), 10, replace = TRUE))
)
# Print the data frame
df
```

## Take the mean of a variable in a dataframe
```{r, warning=FALSE}
mean(pull(df, vec_sample))
mean(pull(df, vec_logical))
mean(pull(df, vec_char))
mean(pull(df, vec_factor))
```

When taking the mean of each variable in the dataframe, the numeric and logical variables work. However, the character vector and factor vector do not work, because it produces NA values.

